---
title: "Project1"
author: "Group 8"
output:
  html_document: default
  pdf_document: default
---


## Prepare
```{r}
library(clValid)
library(factoextra)
library(ClusterR)
```

## Task1-Data1

Read data
```{r}
df=read.csv('Data1.csv')
df_scale=scale(df[2:4])
```

Use kmeans
```{r}
fviz_nbclust(df_scale,kmeans,method = "wss")+labs(subtitle = "X")
km <- kmeans(df_scale,centers=7,nstart=100)
```

Kmeans external validation result
```{r}
km.clusters <- km$cluster
df <- cbind(df, Cluster = km.clusters)
result=external_validation(df$Class, df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```

Use hierarchical clustering
```{r}
df_dist=dist(df_scale)
hclust_avg <- hclust(df_dist, method = 'average')
cut_avg <- cutree(hclust_avg, k = 7)
```

Hierarchical clustering external validation result
```{r}
cut_df <- cbind(df, Cluster = cut_avg)
result=external_validation(cut_df$Class, cut_df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```

Plot original class data
```{r}
fviz_cluster(list(data = df,cluster = df$Class))
```

Plot data allocated by kmeans
```{r}
fviz_cluster(list(data = df,cluster = km.clusters))
```

Plot data allocated by hierarchical clustering
```{r}
fviz_cluster(list(data = df,cluster = cut_avg))
```

## Task1-Data2

Read data
```{r}
df2=read.csv('Data2.csv')[2:5]
df2_scale=distance(df2[1:3])
df2_dist=dist(df2[1:3])
```

Use kmeans
```{r}
fviz_nbclust(df2_scale,kmeans,method = "wss")+labs(subtitle = "X")
km <- kmeans(df2,centers=3, nstart = 100)
km.clusters <- km$cluster
```

Kmeans external validation result
```{r}
km_df <- cbind(df2, Cluster = km.clusters)
result=external_validation(km_df$Class, km_df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```

Use hierarchical clustering
```{r}
hclust_avg <- hclust(df2_dist, method = 'centroid')
cut_avg <- cutree(hclust_avg, k = 4)
```

Hierarchical clustering external validation result
```{r}
cut_df <- cbind(df2, Cluster = cut_avg)
result=external_validation(cut_df$Class, cut_df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```

Plot original class data
```{r}
fviz_cluster(list(data = df2,cluster = df2$Class))
```

Plot data allocated by kmeans
```{r}
fviz_cluster(list(data = df2,cluster = km.clusters))
```

Plot data allocated by hierarchical clustering
```{r}
fviz_cluster(list(data = df2,cluster = cut_avg))
```

## Task1-Data3

Read data
```{r}
df3=read.csv('Data3.csv')[2:5]
df3_scale=scale(df3[1:3])
df3_dist=dist(df3[1:3])
```

Use kmeans
```{r}
fviz_nbclust(df3_scale,kmeans,method = "wss")+labs(subtitle = "X")
km <- kmeans(df3_scale,centers=4)
km.clusters <- km$cluster
```

Kmeans external validation result
```{r}
km_df <- cbind(df3, Cluster = km.clusters)
result=external_validation(km_df$Class, km_df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```

Use hierarchical clustering
```{r}
hclust_avg <- hclust(df3_dist, method = 'average')
cut_avg <- cutree(hclust_avg, k = 4)
```

Hierarchical clustering external validation result
```{r}
cut_df <- cbind(df3, Cluster = cut_avg)
result=external_validation(cut_df$Class, cut_df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```

Plot original class data
```{r}
fviz_cluster(list(data = df3,cluster = df3$Class))
```

Plot data allocated by kmeans
```{r}
fviz_cluster(list(data = df3,cluster = km.clusters))
```

Plot data allocated by hierarchical clustering
```{r}
fviz_cluster(list(data = df3,cluster = cut_avg))
```

## Task1-Data4

Read data
```{r}
df=read.csv('Data4.csv')
df_scale=scale(df[2:4])
```
Use kmeans
```{r}
fviz_nbclust(df_scale,kmeans,method = "wss")+labs(subtitle = "X")
km <- kmeans(df_scale,centers=2,nstart=100)
```
Kmeans external validation result
```{r}
km.clusters <- km$cluster
df <- cbind(df, Cluster = km.clusters)
result=external_validation(df$Class, df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```
Use hierarchical clustering
```{r}
df_dist=dist(df)
hclust_avg <- hclust(df_dist, method = 'median')
cut_avg <- cutree(hclust_avg,2)
```
Hierarchical clustering external validation result
```{r}
cut_df <- cbind(df, Cluster = cut_avg)
result=external_validation(cut_df$Class, cut_df$Cluster, method = "jaccard_index")
print(paste("External validation result =",result))
```

Plot original class data
```{r}
fviz_cluster(list(data = df[2:4],cluster = df$Class))
```
Plot data allocated by kmeans
```{r}
fviz_cluster(list(data = df[2:4],cluster = km.clusters))
```
Plot data allocated by hierarchical clustering
```{r}
fviz_cluster(list(data = df[2:4],cluster = cut_avg))
```